Containers and R---the Rockerverse and beyond

### 2020-01-10 manuscript.Rmd
Remove section headline and add overview sentence

@@

# R Packages
<!-- from packages closer to Docker to second level packages to more complex ones -->

@@

# Use cases and applications

>>>>

The article continues with a brief introduction of containerization basics and the Rocker Project, followed by descriptions of projects developing images with R installations.
Then, we present applications, starting with the R packages specificly for interacting with Docker, second-level packages using containers mediately or only for specific features, up to complex use cases leveraging containers.
We conclude with a reflection on the landscape of packages and applications and point out future directions of development.

@@

# Use cases and applications
<!-- from packages closer to Docker to second level packages to more complex use cases -->

@@
